CLT Results

### 2022-04-21 analysis/clt_irt_analysis.Rmd
add model parameters

```{r}
prior_3pl_fixed <- 
  prior("normal(0, 2)", class = "b", nlpar = "eta") +
  prior("normal(0, 1)", class = "b", nlpar = "logalpha") +
  prior("normal(0, 1)", class = "sd", group = "subjID", nlpar = "eta") + 
  prior("normal(0, 3)", class = "sd", group = "targetWord", nlpar = "eta") +
  prior("normal(0, 1)", class = "sd", group = "targetWord", nlpar = "logalpha")
```

```{r}
irt3 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (1 |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (1 |i| targetWord),
    nl = TRUE
  ),
  prior = prior_va_3pl,
  control = list(adapt_delta = 0.9),
  cores = 6,
  chains = 6,
  iter = 6000
)

@@

```{r}
traceline <- NULL
for(i in 1:46){
extr.2 <- extract.item(firt2, i)
Theta <- matrix(seq(-6,6, by = .1))
traceline[[i]] <- probtrace(extr.2, Theta)
}

@@

```{r}
params%>%left_join(coefs2PL)%>%
  mutate(slope = ifelse(nlpar == "Easiness", -1,1))%>%
  ggplot(aes(x = Estimate, y = par))+
  geom_abline(aes(slope = slope, intercept = 0), lty = 3, alpha = .5)+
  geom_errorbar(aes(ymin = CI_2.5, ymax = CI_97.5), alpha = .25, col = "dodgerblue")+
  geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), alpha = .25, col = "dodgerblue")+
  geom_point(pch = 1, alpha = .75)+
  facet_grid(~nlpar)+
  labs(x = "Bayesian estimate", y = "Frequentist estimate")+
  stat_cor()+
  ylim(-10,10)+
  xlim(-10,10)+
  #coord_fixed(ratio = 1)+
  scale_color_viridis_c()+
  theme_bw()
```

>>>>

```{r}
prior_va_3pl <- 
  prior("normal(0, 2)", class = "b", nlpar = "eta") +
  prior("normal(0, 1)", class = "b", nlpar = "logalpha") +
  prior("normal(0, 1)", class = "sd", group = "subjID", nlpar = "eta") + 
  prior("normal(0, 3)", class = "sd", group = "targetWord", nlpar = "eta") +
  prior("normal(0, 1)", class = "sd", group = "targetWord", nlpar = "logalpha")
```

```{r}
irt3 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (1 |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (1 |i| targetWord),
    nl = TRUE
  ),
  prior = prior_va_3pl,
  control = list(adapt_delta = 0.99, max_treedepth = 12),
  cores = 6,
  chains = 6,
  iter = 6000
)

@@

```{r}
traceline <- NULL
for(i in 1:47){
extr.2 <- extract.item(firt2, i)
Theta <- matrix(seq(-6,6, by = .1))
traceline[[i]] <- probtrace(extr.2, Theta)
}

@@

```{r}
params%>%left_join(coefs2PL)%>%
  #filter(item != "star")%>%
  mutate(slope = ifelse(nlpar == "Easiness", -1,1))%>%
  ggplot(aes(x = Estimate, y = par))+
  geom_abline(aes(slope = slope, intercept = 0), lty = 3, alpha = .5)+
  geom_errorbar(aes(ymin = CI_2.5, ymax = CI_97.5), alpha = .25, col = "dodgerblue")+
  geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), alpha = .25, col = "dodgerblue")+
  geom_point(pch = 1, alpha = .75)+
  facet_grid(~nlpar)+
  labs(x = "Bayesian estimate", y = "Frequentist estimate")+
  stat_cor()+
  #ylim(-10,10)+
  #xlim(-10,10)+
  #coord_fixed(ratio = 1)+
  scale_color_viridis_c()+
  theme_bw()
```
